---
title: "Personal Corona"
output: html_document
---

```{r}
library(tidyverse)
```

```{r}
discount_rate <- 0.05
yrs_from_now_to_end <- 50
yrs <- 0:(yrs_from_now_to_end - 1)
raw_discounted_values <- 1 / ((1 + discount_rate) ^ yrs)
discounted_values <- raw_discounted_values / sum(raw_discounted_values)
cumulative_values <- cumsum(discounted_values)

df.discounted_values = data.frame(yrs, discounted_values, cumulative_values)

df.discounted_values

discounted_values <- df.discounted_values %>%
  ggplot(aes(yrs, discounted_values)) +
  geom_col() +
  ggtitle("How much of the value of the rest of my life will I get per year?")

cumulative_values <- df.discounted_values %>%
  ggplot(aes(yrs, cumulative_values)) +
  geom_col() +
  ggtitle("How much of the value of the rest of my life will I have gotten by X yrs from now?")

discounted_values
cumulative_values

ggsave("discounted_values.jpeg", plot=discounted_values)
ggsave("cumulative_values.jpeg", plot=cumulative_values)
```


# Find: cfr.30to39.men

## cfr.30to39.men = dead.30to39.men/infected.30to39.men

### dead.30to39.men
dead.30to39.men = dead.30to39 * dead.30to39.men/dead.30to39

Assume:
dead.30to39.men/dead.30to39 = dead.men/dead

then dead.30to39.men = dead.30to39 * dead.men/dead

```{r}
dead.30to39<-18
dead.men<-653
dead<-1023

dead.30to39.men<-dead.30to39 * dead.men/dead

dead.30to39.men
```

### infected.30to39.men
infected.30to39.men = infected.30to39 * infected.30to39.men/infected.30to39

Assume:
infected.30to39.men/infected.30to39 = infected.men/infected

then infected.30to39.men = infected.30to39 * infected.men/infected

```{r}
infected.30to39<-7600
infected.men<-22981
infected<-44672

infected.30to39.men<-infected.30to39 * infected.men/infected

infected.30to39.men
```

### cfr.30to39.men = dead.30to39.men/infected.30to39.men

```{r}
cfr.30to39.men<-dead.30to39.men/infected.30to39.men
cfr.30to39.men
```

### faster way
cfr.30to39.men = dead.30to39.men/infected.30to39.men
= (dead.30to39 * dead.men/dead) / (infected.30to39 * infected.men/infected)
= (dead.30to39 * male.proportion_of_dead) / (infected.30to39 * male.proportion_of_infected)
= cfr.30to39 * (male.proportion_of_dead / male.proportion_of_infected)
```{r}
cfr.30to39<-18/7600 # using raw numbers to avoid losing info to rounding
male.proportion_of_dead<-0.638
male.proportion_of_infected<-0.514

cfr.30to39.men <- cfr.30to39 * (male.proportion_of_dead / male.proportion_of_infected)
cfr.30to39.men
```